---
title: "P8105 Homework 1"
author: "Tianqing Wang"
date: "2026-09-26"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
```
#Problem 1

```{r load_penguins}
data("penguins", package = "palmerpenguins")
```

The penguins dataset contains data on penguins species, island, bill length, bill depth, flipper length, body mass, sex and year. The species include "Adelie, Chinstrap, Gentoo".
The dataset contains `r nrow(penguins)` observations and `r ncol(penguins)` variables.
The mean flipper length is `r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 1)` mm.

```{r penguins_scatterplot}
ggplot(penguins, aes(x=bill_length_mm, y=flipper_length_mm, color = species))+geom_point()
ggsave("penguins_scatterplot.png")
```

## Problem 2
```{r create_dataframe}
problem2_df = tibble(
  random_sample = rnorm(10),
  sample_positive = random_sample > 0,
  character_vector = c(
    "a", "b", "c", "d", "e",
    "f", "g", "h", "i", "j"
  ),
  factor_vector = factor(
    c(
      "level1", "level1", "level1",
      "level2", "level2", "level2",
      "level3", "level3", "level3", "level3"
    )
  )
)

problem2_df
```

```{r calculate_means}
mean(pull(problem2_df, random_sample))
mean(pull(problem2_df, sample_positive))
mean(pull(problem2_df, character_vector))
mean(pull(problem2_df, factor_vector))
```

```{r coercion, results='hide', warning=FALSE}
as.numeric(pull(problem2_df, sample_positive))
as.numeric(pull(problem2_df, character_vector))
as.numeric(pull(problem2_df, factor_vector))
```

Converting the logical variable to numeric changes `TRUE` to 1 and `FALSE` to 0, which explains why taking the mean of the logical variable works.

Converting the character variable to numeric does not produce meaningful numeric values because the character strings cannot be interpreted as numbers.

Converting the factor variable to numeric returns the underlying integer codes for the factor levels rather than meaningful quantitative values.

